---
title: "mESCs-analysis-final"
author: "Belinda Phipson"
date: "17/02/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This analysis combines four different mouse ESCs datasets, all generated from different labs. There are two full-length (Kolodziejczyk et al 2015, Buettner et al, 2015) and two UMI datasets (Zeigenhain et al 2016, SCRB-Seq, Grun et al, 2014, CEL-Seq).

# Load R libraries, and useful R functions

```{r,libraries,cache=FALSE}
library(edgeR)
library(RColorBrewer)
library(org.Mm.eg.db)
library(limma)
library(scran)
```
```{r,myRfunctions}
source("/group/bioi1/belinda/SingleCell/Normalisation/normCounts.R")
```
```{r}
ggplotColors <- function(g){

  d <- 360/g

  h <- cumsum(c(15, rep(d,g - 1)))

  hcl(h = h, c = 100, l = 65)

}
```

# Reading in the datasets

```{r}
# Read in Kolodziejczyk
load("./mESCs-data/kol.Rdata")

# Read in Buettner data
load("./mESCs-data/buett.Rdata")

# Read in Grun data
load("./mESCs-data/grun.Rdata")

# Read in Zeigenhain data
load("./mESCs-data/zeig.Rdata")

# load mm10 gene length information
mm10.length <- read.table("mm10-length.txt",header=TRUE,stringsAsFactors = FALSE)
```

# Combine data together for MDSplot
```{r}
# First combine full-length data
m <- match(rownames(y.buett),rownames(y.kol))
full.data <- cbind(y.buett$counts[!is.na(m),],y.kol$counts[m[!is.na(m)],])
rownames(full.data) <- y.buett$genes$gene_id[!is.na(m)]

# Then combine UMI data
m <- match(y.grun$genes$gene_id,y.zeig$genes$gene_id)
umi.data <- cbind(y.grun$counts[!is.na(m),],y.zeig$counts[m[!is.na(m)],])
rownames(umi.data) <- y.grun$genes$gene_id[!is.na(m)]

# Combine full and UMI
m <- match(rownames(umi.data),rownames(full.data))
all.data <- cbind(umi.data[!is.na(m),],full.data[m[!is.na(m)],])

datasets <- rep(c("Grun-UMI-J1","Zeig-UMI-J1","Buettner-Full-Rex1","Kolodz-Full-G4"),c(ncol(y.grun),ncol(y.zeig),ncol(y.buett),ncol(y.kol)))

prot <- rep(c("umi","full-length"),c(ncol(y.grun)+ncol(y.zeig),ncol(y.buett)+ncol(y.kol)))


table(datasets)

```

```{r}
par(mfrow=c(1,2))
par(mar=c(5,5,2,2))
plotMDS.DGEList(DGEList(all.data),pch=c(1,4)[factor(prot)],col=ggplotColors(4)[factor(datasets)],gene.selection = "common",cex.axis=1.2,cex.lab=1.5)
legend("topleft",legend=levels(factor(datasets)),fill=ggplotColors(4))
legend("top",legend=levels(factor(prot)),pch=c(1,4))

media <- c(as.character(y.grun$samples$group),rep("serum+2i",ncol(y.zeig)),rep("Std2i",ncol(y.buett)),as.character(y.kol$samples$group))
media2 <- media
media2[media=="2i" | media=="standard 2i media + LIF"] <- c("Std2i")
media2[media=="serum" | media=="serum + LIF"] <- c("serum")
media2[media=="alternative 2i media + LIF"] <- c("Alt2i")
         

plotMDS.DGEList(DGEList(all.data),pch=c(1:3,22)[factor(datasets)],col=ggplotColors(4)[factor(media2)],gene.selection = "common",dim=c(2,3),cex.axis=1.2,cex.lab=1.5)
legend("bottomleft",legend=levels(factor(media2)),col=ggplotColors(4),pch=16)
legend("bottomright",legend=levels(factor(datasets)),pch=c(1:3,22),cex=0.8)


# check cell type
cell.type <- datasets
cell.type[grep("J1",datasets)] <- "J1"
cell.type[grep("Rex1",datasets)] <- "Rex1"
cell.type[grep("G4",datasets)] <- "G4"

zeig.rep <- rep(NA,ncol(y.zeig))
zeig.rep[grep("SCRBseqA",colnames(y.zeig))] <- "Zeig-UMI-J1-RepA"
zeig.rep[grep("SCRBseqB",colnames(y.zeig))] <- "Zeig-UMI-J1-RepB"
datasets2 <- datasets
datasets2[datasets=="Zeig-UMI-J1"] <- zeig.rep

par(mfrow=c(1,2))
plotMDS.DGEList(DGEList(all.data),pch=c(1:3,15,22)[factor(datasets2)],col=ggplotColors(4)[factor(media2)],gene.selection = "common",dim=c(2,3),cex.axis=1.2,cex.lab=1.5)
legend("bottomleft",legend=levels(factor(media2)),col=ggplotColors(4),pch=16)
legend("bottomright",legend=levels(factor(datasets2)),pch=c(1:3,15,22),cex=0.8)
title("Coloured by media")

plotMDS.DGEList(DGEList(all.data),pch=c(1:3,15,22)[factor(datasets2)],col=ggplotColors(3)[factor(cell.type)],gene.selection = "common",dim=c(2,3),cex.axis=1.2,cex.lab=1.5)
legend("bottomleft",legend=levels(factor(cell.type)),col=ggplotColors(3),pch=16)
legend("bottomright",legend=levels(factor(datasets2)),pch=c(1:3,15,22),cex=0.8)
title("Coloured by mESC cell line")
```

# Gene length figures
## Figure 3

```{r}
pdf(file="./figuresForPaper/Fig3-mESCs.pdf",width=11,height=8)

par(mar=c(5,5,2,2))
par(mfrow=c(2,3))
par(mgp=c(3,1,0))

plotMDS.DGEList(DGEList(all.data),pch=c(1,4)[factor(prot)],col=ggplotColors(8)[5:8][factor(datasets)],gene.selection = "common",cex.axis=1.2,cex.lab=1.5)
legend("topleft",legend=levels(factor(datasets)),fill=ggplotColors(8)[5:8])
legend("bottom",legend=levels(factor(prot)),pch=c(1,4))
title("(a) Coloured by dataset",cex.main=1.5)

plotMDS.DGEList(DGEList(all.data),pch=c(1:3,15,22)[factor(datasets2)],col=ggplotColors(8)[1:4][factor(media2)],gene.selection = "common",dim=c(2,3),cex.axis=1.2,cex.lab=1.5,xlim=c(-1.5,2.35))
legend("bottomleft",legend=levels(factor(media2)),col=ggplotColors(8)[1:4],pch=16)
legend("bottomright",legend=levels(factor(datasets2)),pch=c(1:3,15,22),cex=0.8)
title("(b) Coloured by media",cex.main=1.5)

par(mar=c(8.5,4.5,3,2))
load("./figuresForPaper/fig1A.Rdata")
boxplot(rowMeans(lcpm)~decile,ylab="AvgLogCounts",cex.lab=1.5,cex.axis=1.2,names=labels,las=2,ylim=c(0,12),col=ggplotColors(8)[7])
title("(c) Kolodziejczyk, C1 full-length",cex.main=1.5)
title(xlab="Gene length",cex.lab=1.5,line=7)
abline(h=median(rowMeans(lcpm)[decile==1]),col=colors()[322],lty=5)


load("./figuresForPaper/Buett-genelength.Rdata")
boxplot(rowMeans(lcpm)~decile,ylab="AvgLogCounts",cex.lab=1.5,cex.axis=1.2,names=labels,las=2,ylim=c(0,12),col=ggplotColors(8)[5])
title("(d) Buetnner, C1 full-length",cex.main=1.5)
title(xlab="Gene length",cex.lab=1.5,line=7)
abline(h=median(rowMeans(lcpm)[decile==1]),col=colors()[322],lty=5)

load("./figuresForPaper/Grun-fig2Ai.Rdata")
boxplot(rowMeans(lcpm)~decile,ylab="AvgLogCounts",cex.lab=1.5,cex.axis=1.2,names=labels,las=2,ylim=c(-0.05,3),col=ggplotColors(8)[6])
title("(e) Grun, CEL-Seq UMI",cex.main=1.5)
title(xlab="Gene length",cex.lab=1.5,line=7)
abline(h=median(rowMeans(lcpm)[decile==1]),col=colors()[322],lty=5)

load("./figuresForPaper/Zeig-fig2Aii.Rdata")
boxplot(rowMeans(lcpm)~decile,ylab="AvgLogCounts",cex.lab=1.5,cex.axis=1.2,names=labels,las=2,ylim=c(-0.07,3),col=ggplotColors(8)[8])
title("(f) Zeigenhain, SCRB-seq UMI",cex.main=1.5)
title(xlab="Gene length",cex.lab=1.5,line=7)
abline(h=median(rowMeans(lcpm)[decile==1]),col=colors()[322],lty=5)

dev.off()
```

# Genes present in UMI vs full-length

There are 188 genes detected in both UMI datasets that are not detected in both full-length datasets. These tend to be a bit shorter compared to the background distribution. The 2644 genes detected only in full-length and not in UMI tend to be a bit longer than the UMI genes, and look quite similar to the background.

```{r}
# Supplementary figure?
umi.unq <- rownames(umi.data)[!(rownames(umi.data) %in% rownames(full.data))]
full.unq <- rownames(full.data)[!(rownames(full.data) %in% rownames(umi.data))]
overlap <- rownames(umi.data)[rownames(umi.data) %in% rownames(full.data)]

umi.unq.length <- y.grun$genes$length[match(umi.unq,y.grun$genes$gene_id)]
full.unq.length <- y.buett$genes$length[match(full.unq,y.buett$genes$gene_id)]
overlap.length <- y.grun$genes$length[match(overlap,y.grun$genes$gene_id)]

all_ids <- unique(c(rownames(y.kol),rownames(y.buett),rownames(y.zeig),y.grun$genes$ensembl_id))

ens <- toTable(org.Mm.egENSEMBL2EG)
m <- match(all_ids,ens$ensembl_id)
all_ids_EG <- ens$gene_id[m]
```
```{r}
pdf(file="./figuresForPaper/SuppFig1.pdf",width=9,height=7)
par(mfrow=c(1,1))
par(mar=c(5,5,2,2))
plot(density(log10(mm10.length$Length[match(all_ids,mm10.length$EnsID)])),lwd=2,col=1,lty=2,main="",xlab="Log10(Gene length)",cex.lab=1.5,cex.axis=1.2,ylim=c(0,1.35))
lines(density(log10(umi.unq.length)),lwd=2,col="blue")
lines(density(log10(full.unq.length)),lwd=2,col="red")
lines(density(log10(overlap.length)),lwd=2,col="grey")
legend("topleft",legend=c("Detected in any (n=13434)","Unique to UMI (n=188)","Unique to full-length (n=2644)","Overlap (n=8678)"),lwd=2,col=c(1,4,2,"grey"),lty=c(2,1,1,1))
dev.off()
```

```{r}
lcpm.umi <- normCounts(DGEList(umi.data),log=TRUE,prior.count=1)
lcpm.full <- normCounts(DGEList(full.data),log=TRUE,prior.count=1)

boxplot(rowMeans(lcpm.umi),rowMeans(lcpm.umi)[match(umi.unq,rownames(lcpm.umi))],
        rowMeans(lcpm.umi)[match(overlap,rownames(lcpm.umi))],
        rowMeans(lcpm.full),rowMeans(lcpm.full)[match(full.unq,rownames(lcpm.full))],
        rowMeans(lcpm.full)[match(overlap,rownames(lcpm.full))],
        ylab="Average log counts",col=c(4,4,"grey",2,2,"grey"),
        names=c("All UMI","UMI unique","UMI overlap","All Full","Full unique","Full overlap"),
        cex.lab=1.5,cex.axis=1)

```

```{r}
vennDiagram(cbind(all_ids_EG %in% rownames(umi.data),all_ids_EG %in% rownames(full.data)),names=c("UMI","full-length"),circle.col=c(4,2))
title("Detection rate",cex.main=2)
```

```{r}
pdf(file="./figuresForPaper/DetectionRateFig.pdf",width=12,height=4)
par(mfrow=c(1,3))
par(mar=c(4,4,2,2))
vennDiagram(cbind(all_ids_EG %in% rownames(umi.data),all_ids_EG %in% rownames(full.data)),names=c("UMI","full-length"),circle.col=c(4,2))
title("(a) Detection rate",cex.main=2)
par(mar=c(5,5,2,2))
plot(density(log10(mm10.length$Length[match(all_ids,mm10.length$EnsID)])),lwd=2,col=1,lty=2,main="",xlab="Log10(Gene length)",cex.lab=1.5,cex.axis=1.2,ylim=c(0,1.35))
lines(density(log10(overlap.length)),lwd=2,col="grey")
lines(density(log10(umi.unq.length)),lwd=2,col="blue")
lines(density(log10(full.unq.length)),lwd=2,col="red")
legend("topleft",legend=c("Detected in any (n=13434)","Unique to UMI (n=188)","Unique to full-length (n=2644)","Overlap (n=8678)"),lwd=2,col=c(1,4,2,"grey"),lty=c(2,1,1,1),cex=0.8,bty="n")
title("(b) Gene length density",cex.main="2")
par(mar=c(6,5.5,2,2))
boxplot(rowMeans(lcpm.umi),rowMeans(lcpm.umi)[match(umi.unq,rownames(lcpm.umi))],
        rowMeans(lcpm.umi)[match(overlap,rownames(lcpm.umi))],
        rowMeans(lcpm.full),rowMeans(lcpm.full)[match(full.unq,rownames(lcpm.full))],
        rowMeans(lcpm.full)[match(overlap,rownames(lcpm.full))],
        ylab="Average log counts",col=c(4,4,"grey",2,2,"grey"),
        names=c("All UMI","UMI unique","UMI overlap","All Full","Full unique","Full overlap"),
        cex.lab=1.5,cex.axis=1,las=2)
title("Unique genes: Average log-counts",cex.main=2)
dev.off()
```

```{r}
pdf(file="./figuresForPaper/SuppFig1.pdf",width=7,height=7)
par(mfrow=c(1,1))
par(mar=c(6,5.5,2,2))
boxplot(rowMeans(lcpm.umi),rowMeans(lcpm.umi)[match(umi.unq,rownames(lcpm.umi))],
        rowMeans(lcpm.umi)[match(overlap,rownames(lcpm.umi))],
        rowMeans(lcpm.full),rowMeans(lcpm.full)[match(full.unq,rownames(lcpm.full))],
        rowMeans(lcpm.full)[match(overlap,rownames(lcpm.full))],
        ylab="Average log counts",col=c(4,4,"grey",2,2,"grey"),
        names=c("All UMI","UMI unique","UMI overlap","All Full","Full unique","Full overlap"),
        cex.lab=1.5,cex.axis=1,las=2)
title("Unique genes: Average log-counts",cex.main=2)
dev.off()

```


```{r}
# wilcoxon rank sum test for shift in location of length unique genes
wilcox.test(log10(umi.unq.length),log10(full.unq.length))
```


## GO analysis of unique UMI and full-length genes

```{r}
# Get median gene length in each GO category
ens <- toTable(org.Mm.egENSEMBL2EG)
go <- toTable(org.Mm.egGO2ALLEGS)
d <- duplicated(go[,c("gene_id", "go_id", "Ontology")])
go <- go[!d, ]
m <- match(go$gene_id,ens$gene_id)
test <- data.frame(go,ens[m,])

m <- match(test$ensembl_id,mm10.length$EnsID)
test$length <- mm10.length$Length[m]
head(test)
test <- test[!is.na(test$length),]
# Median gene length in each GO category
avg.go.length <- tapply(test$length,test$go_id,median)
par(mar=c(5,4,2,2))
plot(density(log10(avg.go.length)))
```
```{r}
go.unq.umi <- goana(de=umi.unq,universe=rownames(umi.data),species="Mm")
m <- match(rownames(go.unq.umi),names(avg.go.length))
go.unq.umi$length <- avg.go.length[m]

go.unq.umi <- go.unq.umi[go.unq.umi$N>=10,]
topGO(go.unq.umi)
median(go.unq.umi$length)
quantile(go.unq.umi$length,probs=0.05)

go.unq.full <- goana(de=full.unq,universe = rownames(full.data),species="Mm")
m <- match(rownames(go.unq.full),names(avg.go.length))
go.unq.full$length <- avg.go.length[m]
go.unq.full <- go.unq.full[go.unq.full$N>=10,]
topGO(go.unq.full)
median(go.unq.full$length)
quantile(go.unq.umi$length,probs=0.05)
table(topGO(go.unq.full)$length <quantile(go.unq.umi$length,probs=0.05))
table(topGO(go.unq.full,n=111)$length > 10000)

table(p.adjust(go.unq.full$P.DE,method="fdr") < 0.05)
table(p.adjust(go.unq.umi$P.DE,method="fdr") < 0.05)

go.sig.full <- rownames(topGO(go.unq.full,n=111))
go.sig.umi <- rownames(topGO(go.unq.umi,n=26))
all.sig.go <- unique(c(go.sig.full,go.sig.umi)) 

par(mfrow=c(1,2))
par(mar=c(4.5,4.5,2,2))
vennDiagram(cbind(all.sig.go %in% go.sig.umi,all.sig.go %in% go.sig.full),names=c("UMI","Full-length"),circle.col=c(4,2))
title("Overlap of GO categories",cex.main=2)
plot(density(log10(topGO(go.unq.umi,n=26)$length)),ylim=c(0,5),col=4,lwd=2,main="",xlab="log10(median GO category length",cex.lab=1.5,cex.axis=1.2,cex.main=2)
lines(density(log10(topGO(go.unq.full,n=111)$length)),col=2,lwd=2)
```

```{r}
plot(density(log10(topGO(go.unq.umi,n=100)$length)),ylim=c(0,5),col=4,lwd=2,main="Density plot of avg lengths of top 100 GO",xlab="log10(median GO category length",cex.lab=1.5,cex.axis=1.2,cex.main=2,xlim=c(2.6,4.15))
lines(density(log10(topGO(go.unq.full,n=100)$length)),col=2,lwd=2)
abline(v=log10(median(go.unq.umi$length)),lty=2)
legend("topleft",legend=c("UMI","full-length"),lty=1,col=c(4,2))
legend("topleft",legend=c("UMI","full-length"),lty=1,col=c(4,2),lwd=2)
```

```{r}
pdf(file="./figuresForPaper/DetectionRateFig.pdf",width=10,height=10)
par(mfrow=c(2,2))
par(mar=c(4,4,2,2))
vennDiagram(cbind(all_ids_EG %in% rownames(umi.data),all_ids_EG %in% rownames(full.data)),names=c("UMI","full-length"),circle.col=c(4,2))
title("(a) Overlap of detected genes",cex.main=2)
par(mar=c(5,5,2,2))
plot(density(log10(mm10.length$Length[match(all_ids,mm10.length$EnsID)])),lwd=1,col=1,lty=2,main="",xlab="Log10(Gene length)",cex.lab=1.5,cex.axis=1.2,ylim=c(0,1.35))
lines(density(log10(overlap.length)),lwd=2,col="grey")
lines(density(log10(umi.unq.length)),lwd=2,col="blue")
lines(density(log10(full.unq.length)),lwd=2,col="red")
legend("topleft",legend=c("Detected in any (n=13434)","Unique to UMI (n=188)","Unique to full-length (n=2644)","Overlap (n=8678)"),lwd=c(1,2,2,2),col=c(1,4,2,"grey"),lty=c(2,1,1,1),cex=0.8,bty="n")
title("(b) Gene length density",cex.main="2")
par(mar=c(4.5,4.5,2,2))
vennDiagram(cbind(all.sig.go %in% go.sig.umi,all.sig.go %in% go.sig.full),names=c("UMI","Full-length"),circle.col=c(4,2))
title("(c) Unique genes: GO overlap",cex.main=2)
plot(density(log10(topGO(go.unq.umi,n=26)$length)),ylim=c(0,5),col=4,lwd=2,main="",xlab="log10(median GO category length)",cex.lab=1.5,cex.axis=1.2,cex.main=2)
lines(density(log10(topGO(go.unq.full,n=111)$length)),col=2,lwd=2)
title("(d) Significant GO categories ",cex.main=2)
legend("topleft",legend=c("UMI","full-length","Median GO length"),lty=c(1,1,2),col=c(4,2,1),lwd=2)
abline(v=log10(median(go.unq.umi$length)),lty=2)
dev.off()
```

```{r}
go.unq.umi$FDR <- p.adjust(go.unq.umi$P.DE,method="fdr")
go.unq.full$FDR <- p.adjust(go.unq.full$P.DE,method="fdr")
write.csv(topGO(go.unq.umi,n=Inf),file="GO-results-uniqueUMIgenes.csv",quote=FALSE,row.names = TRUE)
write.csv(topGO(go.unq.full,n=Inf),file="GO-results-uniqueFULLgenes.csv",quote=FALSE,row.names = TRUE)
```

# Differential expression analysis between 2i and serum media

## Full-length data

```{r}
media.kol <- as.character(y.kol$samples$group)
table(media.kol)
media.kol[media.kol=="alternative 2i media + LIF"] <- "Alt2i"
media.kol[media.kol=="standard 2i media + LIF"] <- "Std2i"
media.kol[media.kol=="serum + LIF"] <- "serum"

des.kol <- model.matrix(~0+factor(media.kol))
colnames(des.kol) <- levels(factor(media.kol))

y.kol <- estimateDisp(y.kol,des.kol,robust=TRUE)
plotBCV(y.kol)

fit.kol <- glmFit(y.kol,des.kol)
## Use treat to impose logFC cut-off
treat.kol <- glmTreat(fit.kol,contrast=c(0,-1,1),lfc=1)
res.treat.kol <- decideTestsDGE(treat.kol)
summary(res.treat.kol)
plotMD(treat.kol,status = res.treat.kol)
lines(lowess(treat.kol$AveLogCPM,treat.kol$table$logFC),lwd=2,col=4)
topTags(treat.kol)
```

## UMI data

The UMI data needs some form of normalisation for composition bias. The MD plot is a little strange, and simply applying a scaling factor is not going to completely fix the problem. However, I did note that both TMM and scran help somewhat with the composition bias problem.

```{r}
media.grun <- as.character(y.grun$samples$group)
media.grun[media.grun=="2i"] <- "Std2i"
table(media.grun)

des.grun <- model.matrix(~0+factor(media.grun))
colnames(des.grun) <- levels(factor(media.grun))

# Set up SCE object
sce.grun <- newSCESet(countData=y.grun$counts)
sce.grun <- calculateQCMetrics(sce.grun)
sce.grun <- computeSumFactors(sce.grun,cluster=media.grun,sizes=c(5,10,15,20,25))
summary(sizeFactors(sce.grun))
y.scran.grun <- convertTo(sce.grun, type="edgeR")
y.scran.grun$genes <- y.grun$genes

y.scran.grun <- estimateDisp(y.scran.grun,des.grun,robust=TRUE)
plotBCV(y.scran.grun)

fit.scran.grun <- glmFit(y.scran.grun,des.grun)

# Use treat to impose logFC cut-off
treat.grun <- glmTreat(fit.scran.grun,contrast=c(-1,1),lfc=0.5)
res.treat.grun <- decideTestsDGE(treat.grun)
summary(res.treat.grun)
plotMD(treat.grun,status = res.treat.grun)
lines(lowess(treat.grun$AveLogCPM,treat.grun$table$logFC),lwd=2,col=4)
topTags(treat.grun)
```

# Any overlaps with the uniquely detected genes?
```{r}
toptreat.kol <- topTags(treat.kol,n=Inf,p.value=0.05)$table
toptreat.grun <- topTags(treat.grun,n=Inf,p.value = 0.05)$table
sum(umi.unq %in% toptreat.grun$gene_id)
sum(full.unq %in% toptreat.kol$gene_id)
```

# GO analysis of DE genes

```{r}
go.kol <- goana(de=toptreat.kol$gene_id,universe = treat.kol$genes$gene_id,species="Mm")
go.kol$FDR <- p.adjust(go.kol$P.DE,method="fdr")

go.grun <- goana(de=toptreat.grun$gene_id,universe = treat.grun$genes$gene_id,species="Mm")
go.grun$FDR <- p.adjust(go.grun$P.DE,method="fdr")

sum(rownames(go.unq.umi)[go.unq.umi$FDR<0.05] %in% rownames(go.grun)[go.grun$FDR<0.05])

sum(rownames(go.unq.full)[go.unq.full$FDR<0.05] %in% rownames(go.kol)[go.kol$FDR<0.05])

sum(rownames(go.unq.umi)[go.unq.umi$FDR<0.05] %in% rownames(go.kol)[go.kol$FDR<0.05])

sum(rownames(go.unq.full)[go.unq.full$FDR<0.05] %in% rownames(go.grun)[go.grun$FDR<0.05])

sum(rownames(go.grun)[go.grun$FDR<0.05] %in% rownames(go.kol)[go.kol$FDR<0.05])
```


